Confound and control in language experiments

### 2016-08-05 poster-snl2016.tex
bottom edge spacing
latex quotes

\begin{block}{Interesting Interactions}
Complex interactions make completely unconfounded studies difficult. 
For example, marked constructions are generally less frequent than unmarked ones, leading to the claim that observed differences in processing are frequency effects.
Modelling our confounds directly allows us to examine the piecewise contributions from the experimental manipulation and the 'confound'.
\end{block}

@@

Include a 'nuisance' covariate in an appropriate statistical model, such as a mixed-effects model.

@@

>>>>

\begin{block}{Interesting Interactions}
Complex interactions make completely unconfounded studies difficult. 
For example, marked constructions are generally less frequent than unmarked ones, leading to the claim that observed differences in processing are frequency effects.
Modelling our confounds directly allows us to examine the piecewise contributions from the experimental manipulation and the `confound'.

\vspace{.38cm}
\end{block}

@@

Include a `nuisance' covariate in an appropriate statistical model, such as a mixed-effects model.

@@

\vspace{0.4cm}
